---
title: Discover Weekly
author: DanielG
date: '2018-08-12'
slug: discover-weekly
categories: []
tags: []
---
# Copy excel data straight into R dataframes

Quicker than quick...Copy data in excel and straight into an R dataframe! I won't need this data ever again, so why bother saving and loading a file?

```{r warning=FALSE , results='hide'}
read.table(file = "clipboard" , sep = "\t" , header = TRUE)
```

# EDA Part 1: 

```{r echo=FALSE , warning=FALSE , message=FALSE}
library(tidyverse)

data("mtcars")


```


## Data Summarization 

Usually, I use DataExplorer package for EDA. It produces a nice HTML file containing the EDA. ´create_report function´


## Data Summarization - Character

- table() convert factor or character data (categorical data) into counts. Can table singular or multiple categorical inputs and cross-tabulate counts.

- prop.table() modifies the output of table() to proportion.

```{r warning=FALSE , results='hide'}
mtcars %>% 
  select_if(is.character) %>% 
  map(~ table(.) %>% prop.table())
```

## Data Summarization - Numeric

- This combination is best for seeing how many unique observations are contained in numeric data
```{r warning=FALSE , results='hide'}
mtcars %>% 
  select_if(is.numeric) %>% 
  map_df(~ unique(.) %>% length()) %>% 
  gather() %>% 
  arrange(value)
```
